---
title: "Lab 7 Assignment: Group 07"
format:
  html:
    embed-resources: true
editor: visual
author: "Sarah Rosenberg Asmussen (s194689), Mette Bøge Pedersen (s194679), Caroline Amalie Bastholm Jensen (s213427), Jaime Noguera Piera (s233773), Yassine Turki (s231735)"
---

## Import data and libraries

## Data wrangling

We import necessary libraries:

```{r}
#| warning: false
library(tidyverse)
```

Then we import the biopsy data:

```{r}
biopsy <- read_csv("https://wilkelab.org/classes/SDS348/data_sets/biopsy.csv")
biopsy
```

The dataset contains information about biopsies (rows) from breast tumors and description of these, determined by 9 attributes (columns). There is furthermore a column of the patient outcome being either benign or malignant.

## Data analysis

```{r}
biopsy |> 
  ggplot(mapping = aes(x=clump_thickness, 
                       y=uniform_cell_size,
                       color=outcome)) +
  geom_point()
```

The scatter plot above shows how the clump thickness and cell size is related. We see that there is no clear correlation, as the points are scattered very much all over. Instead, we find that the size of the clump and the cell is related to the outcome. Thus, smaller cell size and clump size correlates with a benign outcome, whereas thick clumps and large cells are related to a malignant outcome.
