---
title: "Lab 7 Assignment: Group 07"
format:
  html:
    embed-resources: true
editor: visual
author: "Sarah Rosenberg Asmussen (s194689), Mette Bøge Pedersen (s194679), Caroline Amalie Bastholm Jensen (s213427), Jaime Noguera Piera (s233773), Yassine Turki (s231735)"
---

## Import data and libraries

## Data wrangling

We import necessary libraries:

```{r}
#| warning: false
library(tidyverse)
library(broom)
```

Then we import the biopsy data:

```{r}
biopsy <- read_csv("https://wilkelab.org/classes/SDS348/data_sets/biopsy.csv")
biopsy
```

The dataset contains information about biopsies (rows) from breast tumors and description of these, determined by 9 attributes (columns). There is furthermore a column of the patient outcome being either benign or malignant.

## Data analysis

### Mette

```{r}
biopsy |> 
  ggplot(mapping = aes(x=clump_thickness, 
                       y=uniform_cell_size,
                       color=outcome)) +
  geom_point()
```

<<<<<<< HEAD
## Caroline

```{r}
pca_fit <- biopsy |> 
  select(where(is.numeric)) |>  # retain only numeric columns
  prcomp(scale = TRUE) # do PCA on scaled data
```

```{r}
pca_fit |> 
  augment(biopsy) |>  # add original dataset back in
  ggplot(aes(.fittedPC1, .fittedPC2, color = outcome)) + 
  geom_point(size = 1.5) +
  scale_color_manual(
    values = c(malignant = "red", benign = "darkgreen")
  ) +
  labs(x = "Fitted PC1",
       y = "Fited PC2")
```
=======
The scatter plot above shows how the clump thickness and cell size is related. We see that there is no clear correlation, as the points are
scattered very much all over. Instead, we find that the size of the clump and the cell is related to the outcome. Thus, smaller cell size a


### Sarah

Comparing the relation between the cell size and mitoses in benign and malignant cells. Here we can observe from the figure that the malignant cells have a higher tendency of having a larger cell size while also having a higher mitoses.

```{r}
ggplot(data = biopsy,
       aes(x = uniform_cell_size,
           y = mitoses,
           colour = outcome)) + 
  geom_point() + 
  theme_minimal() + 
  labs(title = "Relation between cell size and mitoses in breast tumor biopsies",
       x = "Uniform Cell Size",
       y = "Mitoses")
```
>>>>>>> 3655bfa4e5da46964e5c2b06e54ce71c4595b340
