---
title: "Lab 2 Assignment: Group 02"
format:
  html:
    embed-resources: true
editor: visual
author: "Sarah Rosenberg Asmussen (s194689), Mette Bøge Pedersen (s194679), Caroline Amalie Bastholm Jensen (s213427), Jaime Noguera Piera (s233773), Yassine Turki (s231735)"
---

## Import data and libraries

## Data wrangling

We import necessary libraries:

```{r}
#| warning: false
library(tidyverse)
```

Then we import the biopsy data:

```{r}
biopsy <- read_csv("https://wilkelab.org/classes/SDS348/data_sets/biopsy.csv")
biopsy
```

The dataset contains information about biopsies (rows) from breast tumors and description of these, determined by 9 attributes (columns). There is furthermore a column of the patient outcome being either benign or malignant.

## Data analysis

### Sarah

Comparing the relation between the cell size and mitoses in benign and malignant cells. Here we can observe from the figure that the malignant cells have a higher tendency of having a larger cell size while also having a higher mitoses.

```{r}
ggplot(data = biopsy,
       aes(x = uniform_cell_size,
           y = mitoses,
           colour = outcome)) + 
  geom_point() + 
  theme_minimal() + 
  labs(title = "Relation between cell size and mitoses in breast tumor biopsies",
       x = "Uniform Cell Size",
       y = "Mitoses")
```
